### 2023-11-03 Scripts/Manuscript/manuscript.Rmd
added the formulas to the manuscript.

# creates a reference list for all used R packages and the installed R version (does not include Rstudio)
r_refs("r-references.bib")
```

@@

<!-- \@ref(sec:measures) didn't work for section corss-reference in the paragraph above-->

@@

### Measurement Error Measures
Two main sources of information were used to test hypothesis 1, the reported reliability coefficient from the replication protocols, and the reported reliability coefficient in the original articles. The reported reliability coefficient is the score reliability reported per measure in the replication protocol or original article. Both the type (Cronbach's alpha, retest, interrater, etc.) and the value itself were extracted.

@@

### Replicability Measure
Hypothesis 3 as well as 5 specify an association between either score reliability or QMPs respectively, and replication success. Replication success was based on the test of the main effect of a study. However, the unit of measurement for the data in this thesis was a measure of a unique variable, not an effect. Fortunately, since only primary measures were included in the data, each measured a variable of the main effect, and as a result the measure remains related to the test of the main effect. Replication was based on the significance of the meta-analytic effect of the replication set as reported in its respective Many Labs report. An effect was considered replicated if the meta-analytic p-value was lower than .05, and in the same direction as the original effect. In all cases, meta-analytic significance of an effect meant that support in the direction of the original effect was found.

@@

### QMP measures
The same data as for the test of hypothesis 2 was used to check for the unidimensionality of the factor structure, as part of the exploratory analyses. A check for unidimensionality as validity evidence only makes sense if the measure was intended to be unidimensional. Therefore, for each replication for which data was available, the protocol was checked to ensure that the scores on each measure were meant to assess a single construct.

### Validity Measure
The same data as for the test of hypothesis 2 was used to check for the unidimensionality of the factor structure, as part of the exploratory analyses. A check for unidimensionality as validity evidence only makes sense if the measure was intended to be unidimensional. Therefore, for each replication for which data was available, the protocol was checked to ensure that the scores on each measure were meant to assess a single construct.

## Analyses
### Analyses Measurement Error
Every hypothesis test in this thesis used an alpha significance cutoff of .05. No correction for multiple testing was applied, to avoid inflating type II error rate. The generally small sample size and consequently low power of these analyses meant that a smaller alpha would increase the number of false negatives. On top of that, these analyses were considered as exploratory. In this exploratory context, the rate of discovery of any potential true effects was given more value relative to decreasing any false positives compared to typical confirmatory research. That as a consequence obtaining false positives was more likely has been accepted, as false negatives were deemed more harmful to this study's aims.

@@

INSERT H2 FORMULA HERE

The purpose of this analysis was to investigate variability in calculated reliability coefficients within and between replication sets. However, to the author’s knowledge no formal test exists as of the writing of this thesis for testing the significance of within group variance after controlling for between group variance. Instead the intraclass correlation (ICC) coefficient was calculated an indicator of within vs. between variability. Formula XXX shows the formula used to calculate the ICC.

INSERT ICC FORMULA HERE

@@

INSERT H3 FORMULA HERE

@@

INSET f(.) FORMULA HERE

@@

### Analyses QMPs
The reported analyses were primarily based on the revised set of QMP data. The results using the original QMP data are mentioned when the results led to different conclusions. The analysis code for both the original and revised QMP data are available in R script on the OSF page of this thesis: <https://osf.io/9r8yt/>.

@@

INSERT BETALINK FORMULA HERE

@@

INSERT H4 FORMULA HERE

@@

INSERT H5 FORMULA HERE

@@

INSERT H6 FORMULA HERE

@@

### Exploratory Analyses
Follow-up analyses were preregistered for hypothesis 6. Using a similar model to the main hypothesis test with all unique combination of the five different QMP types being tested across original and replication data. The goal of these analyses was to see if there are any type specific carry-over effects in QMPs between original and replication. As these analyses are exploratory in nature, due to the large number of tests, the focus was on visualisation rather than inference.

Finally, in order to present additional validity evidence alongside the analyses of Cronbach's alpha and omega coefficients, the unidimensionality of each measure was investigated. To test this, each multiple item scalar measure had their factor structure investigated on the entire measure data of the replication set. A single factor confirmatory factor analysis was implemented using the *fa* function from the *psych* package [@revelle2022psych] in R. The maximum likelihood factoring method was used, with defaults being used for all other function arguments. From this analysis, the RMSEA of the one factor solution was extracted. Additionally, a parallel test was conducted using the *fa.parallel* function also from the psych package. If either the RMSEA score < .08, or the parallel analysis returned a one factor solution, unidimensionality was coded as true, otherwise it was coded as false.

>>>>

# creates a reference list for all used R packages and the installed R version (does not include Rstudio)
r_refs("r-references.bib")

### DON'T FORGET THAT I SHOULD REMOVE HERE THE R PACKAGE REFERENCES FROM MY REFERENCES BIB AND SHOULD HAVE THE R=REFERENCES BIB TAKE CARE OF THAT INSTEAD.
```

@@

<!-- @ref(sec:measures) didn't work for section corss-reference in the paragraph above-->

@@

### Measurement Error Measures

Two main sources of information were used to test hypothesis 1, the reported reliability coefficient from the replication protocols, and the reported reliability coefficient in the original articles. The reported reliability coefficient is the score reliability reported per measure in the replication protocol or original article. Both the type (Cronbach's alpha, retest, interrater, etc.) and the value itself were extracted.

@@

### Replicability Measure

Hypothesis 3 as well as 5 specify an association between either score reliability or QMPs respectively, and replication success. Replication success was based on the test of the main effect of a study. However, the unit of measurement for the data in this thesis was a measure of a unique variable, not an effect. Fortunately, since only primary measures were included in the data, each measured a variable of the main effect, and as a result the measure remains related to the test of the main effect. Replication was based on the significance of the meta-analytic effect of the replication set as reported in its respective Many Labs report. An effect was considered replicated if the meta-analytic p-value was lower than .05, and in the same direction as the original effect. In all cases, meta-analytic significance of an effect meant that support in the direction of the original effect was found.

@@

### QMP measures

The same data as for the test of hypothesis 2 was used to check for the unidimensionality of the factor structure, as part of the exploratory analyses. A check for unidimensionality as validity evidence only makes sense if the measure was intended to be unidimensional. Therefore, for each replication for which data was available, the protocol was checked to ensure that the scores on each measure were meant to assess a single construct.

### Validity Measure

The same data as for the test of hypothesis 2 was used to check for the unidimensionality of the factor structure, as part of the exploratory analyses. A check for unidimensionality as validity evidence only makes sense if the measure was intended to be unidimensional. Therefore, for each replication for which data was available, the protocol was checked to ensure that the scores on each measure were meant to assess a single construct.

## Analyses

### Analyses Measurement Error

Every hypothesis test in this thesis used an alpha significance cutoff of .05. No correction for multiple testing was applied, to avoid inflating type II error rate. The generally small sample size and consequently low power of these analyses meant that a smaller alpha would increase the number of false negatives. On top of that, these analyses were considered as exploratory. In this exploratory context, the rate of discovery of any potential true effects was given more value relative to decreasing any false positives compared to typical confirmatory research. That as a consequence obtaining false positives was more likely has been accepted, as false negatives were deemed more harmful to this study's aims.

@@

```{=tex}
\begin{align*}
& Level 1: alpha_{ij} = \beta_{0j} + e_{ij} \qquad\qquad\quad e_{ij} \sim N(0, \sigma_{e}^{2}) \\
& Level 2: \beta_{0j} = \gamma_{00} + u_{0j} \qquad\qquad\qquad u_{0j} \sim N(0, \sigma_{u0}^{2}) \\
& Mixed: alpha_{ij} = \gamma_{00} + u_{0j} + e_{ij}
\end{align*}
```

The purpose of this analysis was to investigate variability in calculated reliability coefficients within and between replication sets. However, to the author's knowledge no formal test exists as of the writing of this thesis for testing the significance of within group variance after controlling for between group variance. Instead the intraclass correlation (ICC) coefficient was calculated an indicator of within vs. between variability. The formula used to calculate the ICC is presented below.

$$ICC = \frac{u_{0j}}{(e_{ij} + u_{0j})}$$

@@

$$f(replicated_{i}) = \beta_{0} + \beta_{1} alpha_{i}$$

@@

$$f(.) = log\frac{p_{replicated}}{1 - p_{replicated}}$$

@@

### Analyses QMPs

The reported analyses were primarily based on the revised set of QMP data. The results using the original QMP data are mentioned when the results led to different conclusions. The analysis code for both the original and revised QMP data are available in R script on the OSF page of this thesis: <https://osf.io/9r8yt/>.

@@

$$g(.) = (0, 1) \mapsto \mathbb{R}$$

@@

$$g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replication_{i}$$

@@

$$g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replicated_{i}$$

@@

$$g(QMP\_ratio\_replication_{i}) = \beta_{0} + \beta_{1} QMP\_ratio\_original_{i}$$

@@

### Exploratory Analyses

Follow-up analyses were preregistered for hypothesis 6. Using a similar model to the main hypothesis test with all unique combination of the five different QMP types being tested across original and replication data. The goal of these analyses was to see if there are any type specific carry-over effects in QMPs between original and replication. As these analyses are exploratory in nature, due to the large number of tests, the focus was on visualisation rather than inference.

Finally, in order to present additional validity evidence alongside the analyses of Cronbach's alpha and omega coefficients, the unidimensionality of each measure was investigated. To test this, each multiple item scalar measure had their factor structure investigated on the entire measure data of the replication set. A single factor confirmatory factor analysis was implemented using the *fa* function from the *psych* package [@revelle2022psych] in R. The maximum likelihood factoring method was used, with defaults being used for all other function arguments. From this analysis, the RMSEA of the one factor solution was extracted. Additionally, a parallel test was conducted using the *fa.parallel* function also from the psych package. If either the RMSEA score \< .08, or the parallel analysis returned a one factor solution, unidimensionality was coded as true, otherwise it was coded as false.
